SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-20 Chapters/sdm-autocorrelation.tex
SDM Autocorrelation.

As $n \rightarrow \infty \Rightarrow \frac{1}{2^n} \binom{n-1}{n/2} \rightarrow 0$, the proof is done for $n$ even.

>>>>

Stirling's approximation yields that, for $n$ sufficiently large, $\binom{n}{n/2} \sim \frac{2^n}{\sqrt{\pi n/2}}$. Thus, $\frac{1}{2^n} \binom{n}{n/2} \sim \frac{\sqrt{2}}{\sqrt{\pi n}}$, which yields $\lim_{n \rightarrow \infty} \frac{1}{2^n} \binom{n}{n/2} = 0$. Finally, as $\binom{n-1}{n/2} \le \binom{n}{n/2}$, by the squeeze theorem, $\lim_{n \rightarrow \infty} \frac{1}{2^n} \binom{n-1}{n/2} = 0$, which closes the proof for $n$ even.
